%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Collins Aerospace} % Organization
    {Annapolis, MD} % Location
    {Sep. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Provisioned an easily managable hybrid infrastructure(Amazon AWS + On-premise) utilizing IaC(Infrastructure as Code) tools like Ansible, Vcenter and Vagrant.}
        \item {Developed and fielded a highly-secure Python application that enables a bidirectional exchange of data between aircraft and ground operations, including aircraft maintenance and performance data.}
        \item {Documented and demonstrated solutions by developing system design documentation, interface control documents, diagrams and user guides along with commented and clear code.}
        \item {Designed, developed, tested and deployed core software modules and subsystem flight applications per design documents and sequence diagrams.}
        \item {Prepared and installed software virtualization solutions by determining system design specifications and programming standards.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Developer} % Job title
    {Bonzi} % Organization
    {Seattle, WA} % Location
    {Apr. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for design, development, and deployment of web projects for a job recruiting platform.}
        \item {Created software development lifecycle methods for development, staging, and production code workflows.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Percival Engineering} % Organization
    {Ellicott City, MD} % Location
    {Nov. 2016 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted system analysis to discover vulnerabilities in software applications.}
        \item {Responsible for the development and testing of SCADA software.}
        % \item {Extensive use of JIRA, Confluence, and BitBucket for project management.}
        % \item {Defined and documented bug fixes and other test activities.}
        \item {Engaged in bi-weekly agile sprints with an eight-person team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cyber Operations Specialist (17-c) - Security clearance:  TS/SCI} % Job title
    {U.S. Army} % Organization
    {Fort Meade, MD} % Location
    {Nov. 2013 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed software capabilities for offensive cyber operations, vulnerability assessments and penetration testing using manual testing techniques, scripts, commercial and open source tools.}
        \item {Troubleshot and debugged networks, systems, and applications to identify vulnerabilities and other operational defects.}
        \item {Provided feasibility analysis, requirements development, and solution design for computer network operations.}
      \end{cvitems}
    }

\end{cventries}
